Multidimensional signals and analytic flexibility: Estimating degrees of freedom in human speech analyses

### 2022-11-04 RR_manuscript/Draft_RR.Rmd
add author list to rr

---
title: "Multidimensional signals and analytic flexibility: Estimating degrees of freedom in human speech analyses"
runninghead: "Multidimensional signals and analytic flexibility"
author:
- name: Stefano Coretta*
  num: 1, 2
- name: Joseph V. Casillas
  num: 3
- name: Timo B. Roettger
  num: 4
address:
- num: 1
  org: Department of Linguistics and English Language, University of Edinburgh, United Kingdom
- num: 2
  org: Institute of Phonetics and Speech Processing, Ludwig-Maximilian University Munich, Germany
- num: 3
  org: Department of Spanish and Portuguese, Rutgers University, New Brunswick, United States
- num: 4
  org: Department of Linguistics and Scandinavian Studies, University of Oslo, Oslo, Norway
corrauth: "Timo B. Roettger"
email: "timo.b.roettger@iln.uio.no"
abstract: "Recent empirical studies have highlighted the large degree of analytic flexibility in data analysis which can lead to substantially different conclusions based on the same data set. Thus, researchers have expressed their concerns that these researcher degrees of freedom might facilitate bias and can lead to claims that do not stand the test of time. Even greater flexibility is to be expected in fields in which the primary data lend themselves to a variety of possible operationalizations. The multidimensional, temporally extended nature of speech constitutes an ideal testing ground for assessing the variability in analytic approaches, which derives not only from aspects of statistical modeling, but also from decisions regarding the quantification of the measured behavior. In the present study, we gave the same speech production data set to 46 teams of researchers and asked them to answer the same research question, resulting in substantial variability in reported effect sizes and their interpretation. Using Bayesian meta-analytic tools, we further find little to no evidence that the observed variability can be explained by analysts' prior beliefs, expertise or the perceived quality of their analyses. In light of this idiosyncratic variability, we recommend that researchers more transparently share details of their analysis, strengthen the link between theoretical construct and quantitative system and calibrate their (un)certainty in their conclusions"
keywords: "crowdsourcing science, data analysis, scientific transparency, speech, acoustic analysis"
classoption:
  - Review
  - times
bibliography: references
bibliographystyle: sageh
output:
  bookdown::pdf_book:
    base_format: rticles::sage_article
    keep_tex: yes
    template: template.tex
    includes:
      in_header: preamble.tex
---

>>>>

---
title: "Multidimensional signals and analytic flexibility: Estimating degrees of freedom in human speech analyses"
runninghead: "Multidimensional signals and analytic flexibility"
author:
- name: Stefano Coretta*
  num: 1, 2
- name: Joseph V. Casillas
  num: 3
- name: Simon Roessig
- name: Michael Franke
- name: Ali H. Al-Hoorie
- name: Jalal Al-Tamimi
- name: Najd E. Alotaibi
- name: Mohammed K. AlShakhori
- name: Ruth M. Altmiller
- name: Pablo Arantes
- name: Angeliki Athanasopoulou
- name: Melissa M. Baese-Berk
- name: George Bailey
- name: Cheman Baira A Sangma
- name: Eleonora J. Beier
- name: Gabriela M. Benavides
- name: Nicole Benker
- name: Emelia P. BensonMeyer
- name: Nina R. Benway
- name: Grant M. Berry
- name: Liwen Bing
- name: Christina Bjorndahl
- name: Mariska Bolyanatz
- name: Aaron Braver
- name: Violet A. Brown
- name: Alicia M. Brown
- name: Alejna Brugos
- name: Erin M. Buchanan
- name: Tanna Butlin
- name: Andrés Buxó-Lugo
- name: Coline Caillol
- name: Francesco Cangemi
- name: Christopher Carignan
- name: Sita Carraturo
- name: Tiphaine Caudrelier
- name: Eleanor Chodroff
- name: Michelle Cohn
- name: Johanna Cronenberg
- name: Olivier Crouzet
- name: Erica L. Dagar
- name: Charlotte Dawson
- name: Carissa A. Diantoro
- name: Marie Dokovova
- name: Wood Drake
- name: Fengting Du
- name: Margaux Dubuis
- name: Florent Duême
- name: Matthew Durward
- name: Ander Egurtzegi
- name: Mahmoud M. Elsherif
- name: Janina Esser
- name: Emmanuel Ferragne
- name: Fernanda Ferreira
- name: Lauren K. Fink
- name: Sara Finley
- name: Kurtis Foster
- name: Paul Foulkes
- name: Rosa Franzke
- name: Gabriel Frazer-McKee
- name: Robert Fromont
- name: Christina García
- name: Jason Geller
- name: Camille L. Grasso
- name: Pia Greca
- name: Martine Grice
- name: Magdalena S. Grose-Hodge
- name: Amelia J. Gully
- name: Caitlin Halfacre
- name: Westerbeek Hans
- name: Ivy Hauser
- name: Jen Hay
- name: Robert Haywood
- name: Sam Hellmuth
- name: Allison I. Hilger
- name: Nicole Holliday
- name: Damar Hoogland
- name: Yaqian Huang
- name: Vincent Hughes
- name: Ane Icardo Isasa
- name: Zlatomira G. Ilchovska
- name: Hae-Sung Jeon
- name: Jacq Jones
- name: Mágat N. Junges
- name: Stephanie Kaefer
- name: Constantijn Kaland
- name: Matthew C. Kelley
- name: Niamh E. Kelly
- name: Ghada Khattab
- name: Emiel Krahmer
- name: Dorota Krajewska
- name: Andreas Krug
- name: Abhilasha A. Kumar
- name: Anna Lander
- name: Tomas O. Lentz
- name: Wanyin Li
- name: Yanyu Li
- name: Maria Lialiou
- name: Ronaldo M. Lima Jr.
- name: Justin J. H. Lo
- name: Julio César López Otero
- name: Bradley Mackay
- name: Bethany MacLeod
- name: Mel Mallard
- name: Carol-Ann McConnellogue
- name: George Moroz
- name: Mridhula Murali
- name: Ladislas Nalborczyk
- name: Filip Nenadić
- name: Jessica Nieder
- name: Dušan Nikolić
- name: Francisco G. S. Nogueira
- name: Heather M. Offerman
- name: Elisa Passoni
- name: Maud Pélissier
- name: Scott J. Perry
- name: Alexandra M. Pfiffner
- name: Michael Proctor
- name: Ryan Rhodes
- name: Nicole Rodríguez
- name: Elizabeth Roepke
- name: Jan P. Röer
- name: Koolen Ruud
- name: Lucia Sbacco
- name: Rebecca Scarborough
- name: Felix Schaeffler
- name: Erik Schleef
- name: Dominic Schmitz
- name: Alexander Shiryaev
- name: Márton Sóskuthy
- name: Malin Spaniol
- name: Joseph A. Stanley
- name: Alyssa Strickler
- name: Alessandro Tavano
- name: Fabian Tomaschek
- name: Benjamin V. Tucker
- name: Rory Turnbull
- name: Kingsley Ugwuanyi
- name: Iñigo Urrestarazu-Porta
- name: Ruben van de Vijver
- name: Kristin J. Van Engen
- name: Emiel van Miltenburg
- name: Bruce Wang
- name: Natasha Warner
- name: Simon Wehrle
- name: Seth Wiener
- name: Stephen Winters
- name: Sidney G.-J. Wong
- name: Anna Wood
- name: Jane Wottawa
- name: Chenzi Xu
- name: Germán Zárate-Sández
- name: Georgia Zellou
- name: Cong Zhang
- name: Jian Zhu
- name: Timo B. Roettger
  num: 4
address:
- num: 1
  org: Department of Linguistics and English Language, University of Edinburgh, United Kingdom
- num: 2
  org: Institute of Phonetics and Speech Processing, Ludwig-Maximilian University Munich, Germany
- num: 3
  org: Department of Spanish and Portuguese, Rutgers University, New Brunswick, United States
- num: 4
  org: Department of Linguistics and Scandinavian Studies, University of Oslo, Oslo, Norway
corrauth: "Timo B. Roettger"
email: "timo.b.roettger@iln.uio.no"
abstract: "Recent empirical studies have highlighted the large degree of analytic flexibility in data analysis which can lead to substantially different conclusions based on the same data set. Thus, researchers have expressed their concerns that these researcher degrees of freedom might facilitate bias and can lead to claims that do not stand the test of time. Even greater flexibility is to be expected in fields in which the primary data lend themselves to a variety of possible operationalizations. The multidimensional, temporally extended nature of speech constitutes an ideal testing ground for assessing the variability in analytic approaches, which derives not only from aspects of statistical modeling, but also from decisions regarding the quantification of the measured behavior. In the present study, we gave the same speech production data set to 46 teams of researchers and asked them to answer the same research question, resulting in substantial variability in reported effect sizes and their interpretation. Using Bayesian meta-analytic tools, we further find little to no evidence that the observed variability can be explained by analysts' prior beliefs, expertise or the perceived quality of their analyses. In light of this idiosyncratic variability, we recommend that researchers more transparently share details of their analysis, strengthen the link between theoretical construct and quantitative system and calibrate their (un)certainty in their conclusions"
keywords: "crowdsourcing science, data analysis, scientific transparency, speech, acoustic analysis"
classoption:
  - Review
  - times
bibliography: references
bibliographystyle: sageh
output:
  bookdown::pdf_book:
    base_format: rticles::sage_article
    keep_tex: yes
    template: template.tex
    includes:
      in_header: preamble.tex
---

### 2022-11-04 RR_manuscript/Draft_RR.tex
add author list to rr

\author{Stefano Coretta*\affilnum{1, 2}, Joseph V. Casillas\affilnum{3}, Timo B. Roettger\affilnum{4}}

>>>>

\author{Stefano Coretta*\affilnum{1, 2}, Joseph V. Casillas\affilnum{3}, Simon Roessig\affilnum{}, Michael Franke\affilnum{}, Ali H. Al-Hoorie\affilnum{}, Jalal Al-Tamimi\affilnum{}, Najd E. Alotaibi\affilnum{}, Mohammed K. AlShakhori\affilnum{}, Ruth M. Altmiller\affilnum{}, Pablo Arantes\affilnum{}, Angeliki Athanasopoulou\affilnum{}, Melissa M. Baese-Berk\affilnum{}, George Bailey\affilnum{}, Cheman Baira A Sangma\affilnum{}, Eleonora J. Beier\affilnum{}, Gabriela M. Benavides\affilnum{}, Nicole Benker\affilnum{}, Emelia P. BensonMeyer\affilnum{}, Nina R. Benway\affilnum{}, Grant M. Berry\affilnum{}, Liwen Bing\affilnum{}, Christina Bjorndahl\affilnum{}, Mariska Bolyanatz\affilnum{}, Aaron Braver\affilnum{}, Violet A. Brown\affilnum{}, Alicia M. Brown\affilnum{}, Alejna Brugos\affilnum{}, Erin M. Buchanan\affilnum{}, Tanna Butlin\affilnum{}, Andrés Buxó-Lugo\affilnum{}, Coline Caillol\affilnum{}, Francesco Cangemi\affilnum{}, Christopher Carignan\affilnum{}, Sita Carraturo\affilnum{}, Tiphaine Caudrelier\affilnum{}, Eleanor Chodroff\affilnum{}, Michelle Cohn\affilnum{}, Johanna Cronenberg\affilnum{}, Olivier Crouzet\affilnum{}, Erica L. Dagar\affilnum{}, Charlotte Dawson\affilnum{}, Carissa A. Diantoro\affilnum{}, Marie Dokovova\affilnum{}, Wood Drake\affilnum{}, Fengting Du\affilnum{}, Margaux Dubuis\affilnum{}, Florent Duême\affilnum{}, Matthew Durward\affilnum{}, Ander Egurtzegi\affilnum{}, Mahmoud M. Elsherif\affilnum{}, Janina Esser\affilnum{}, Emmanuel Ferragne\affilnum{}, Fernanda Ferreira\affilnum{}, Lauren K. Fink\affilnum{}, Sara Finley\affilnum{}, Kurtis Foster\affilnum{}, Paul Foulkes\affilnum{}, Rosa Franzke\affilnum{}, Gabriel Frazer-McKee\affilnum{}, Robert Fromont\affilnum{}, Christina García\affilnum{}, Jason Geller\affilnum{}, Camille L. Grasso\affilnum{}, Pia Greca\affilnum{}, Martine Grice\affilnum{}, Magdalena S. Grose-Hodge\affilnum{}, Amelia J. Gully\affilnum{}, Caitlin Halfacre\affilnum{}, Westerbeek Hans\affilnum{}, Ivy Hauser\affilnum{}, Jen Hay\affilnum{}, Robert Haywood\affilnum{}, Sam Hellmuth\affilnum{}, Allison I. Hilger\affilnum{}, Nicole Holliday\affilnum{}, Damar Hoogland\affilnum{}, Yaqian Huang\affilnum{}, Vincent Hughes\affilnum{}, Ane Icardo Isasa\affilnum{}, Zlatomira G. Ilchovska\affilnum{}, Hae-Sung Jeon\affilnum{}, Jacq Jones\affilnum{}, Mágat N. Junges\affilnum{}, Stephanie Kaefer\affilnum{}, Constantijn Kaland\affilnum{}, Matthew C. Kelley\affilnum{}, Niamh E. Kelly\affilnum{}, Ghada Khattab\affilnum{}, Emiel Krahmer\affilnum{}, Dorota Krajewska\affilnum{}, Andreas Krug\affilnum{}, Abhilasha A. Kumar\affilnum{}, Anna Lander\affilnum{}, Tomas O. Lentz\affilnum{}, Wanyin Li\affilnum{}, Yanyu Li\affilnum{}, Maria Lialiou\affilnum{}, Ronaldo M. Lima Jr.\affilnum{}, Justin J. H. Lo\affilnum{}, Julio César López Otero\affilnum{}, Bradley Mackay\affilnum{}, Bethany MacLeod\affilnum{}, Mel Mallard\affilnum{}, Carol-Ann McConnellogue\affilnum{}, George Moroz\affilnum{}, Mridhula Murali\affilnum{}, Ladislas Nalborczyk\affilnum{}, Filip Nenadić\affilnum{}, Jessica Nieder\affilnum{}, Dušan Nikolić\affilnum{}, Francisco G. S. Nogueira\affilnum{}, Heather M. Offerman\affilnum{}, Elisa Passoni\affilnum{}, Maud Pélissier\affilnum{}, Scott J. Perry\affilnum{}, Alexandra M. Pfiffner\affilnum{}, Michael Proctor\affilnum{}, Ryan Rhodes\affilnum{}, Nicole Rodríguez\affilnum{}, Elizabeth Roepke\affilnum{}, Jan P. Röer\affilnum{}, Koolen Ruud\affilnum{}, Lucia Sbacco\affilnum{}, Rebecca Scarborough\affilnum{}, Felix Schaeffler\affilnum{}, Erik Schleef\affilnum{}, Dominic Schmitz\affilnum{}, Alexander Shiryaev\affilnum{}, Márton Sóskuthy\affilnum{}, Malin Spaniol\affilnum{}, Joseph A. Stanley\affilnum{}, Alyssa Strickler\affilnum{}, Alessandro Tavano\affilnum{}, Fabian Tomaschek\affilnum{}, Benjamin V. Tucker\affilnum{}, Rory Turnbull\affilnum{}, Kingsley Ugwuanyi\affilnum{}, Iñigo Urrestarazu-Porta\affilnum{}, Ruben van de Vijver\affilnum{}, Kristin J. Van Engen\affilnum{}, Emiel van Miltenburg\affilnum{}, Bruce Wang\affilnum{}, Natasha Warner\affilnum{}, Simon Wehrle\affilnum{}, Seth Wiener\affilnum{}, Stephen Winters\affilnum{}, Sidney G.-J. Wong\affilnum{}, Anna Wood\affilnum{}, Jane Wottawa\affilnum{}, Chenzi Xu\affilnum{}, Germán Zárate-Sández\affilnum{}, Georgia Zellou\affilnum{}, Cong Zhang\affilnum{}, Jian Zhu\affilnum{}, Timo B. Roettger\affilnum{4}}
